\documentclass[12pt]{article}
\usepackage{geometry}
\usepackage{nopageno}
\usepackage{setspace}
\usepackage{hyperref}

\renewcommand{\familydefault}{\sfdefault}

\geometry{
	a4paper,
	left=15mm,
	right=15mm,
	top=20mm,
	bottom=10mm
}

\begin{document}
\begin{center}
	\section*{Letter of Motivation for the Internship at Bang \& Olufsen}
\end{center}
Dear Bang \& Olufsen Team,\\
With much enthusiasm I discovered the open position as an intern in the Bang \& Olufsen audio lab. Through my years of studying audio and electrical engineering, as well as information and computer engineering, I acquired and developed useful skills that I am eager to make use of.

Considering my strong interest in photography and art, next to my passion for all things audio, the commitment to combining cutting-edge technology with great design is one of the things I value a lot about this company.
Additionally, I highly appreciate the ambitious goals regarding both environmental impact and social equity shown in your sustainability report.
\\
As for me, I consider myself very communicative and straight-forward. I highly value helping others where possible, and conversely know when to ask for help as well. I am always eager to learn and do new things, seeing as how I do not like to remain idle for too long.

Programming is one of my core strengths and passions. Mostly in C++, but also other languages, naturally depending on the use case. I offer knowledge in digital signal processing and machine learning. My experience in programming human interface designs is limited, however, only having used \textit{Dear ImGui} and rudimentary HTML/CSS/JS so far. An adequate representation of my current programming skills is seen in the code for my bachelor thesis (\href{https://git.iem.at/aronpetritz/gemupg}{https://git.iem.at/aronpetritz/gemupg}) which was written within two months in C++ using the SDL3 framework. I strived to create a new software environment for music creation, that is inherently polymetric and microtonal and rethinks tracks into two-dimensional areas.

I am proficient in the use of professional audio equipment, having mixed many live concerts. Among other things, I also recorded and mixed an EP for a band consisting of twelve people by myself in our university's studio.
3D audio formats fascinate me, especially ambisonics (to be fair, our university does focus on it, as you probably know), which amplified my motivation to join your team upon reading about the ambisonic listening room. On my various trips abroad I enthusiastically try to convert people to using - or at least looking into - the ambisonics format.

Lastly, I am familiar with the process of acoustic room measurements, having done measurements and calculations even outside of university lectures to improve the acoustics of various environments. Furthermore, I am currently looking into building small spherical coaxial speakers to place above my TV.

This internship represents an invaluable opportunity to learn from a team of experts, hopefully allowing me to grow together with your company, which I can identify with on many levels. I would cement my programming skills within a professional environment while also deepening my understanding of acoustic research.
I am eager to bring my technical expertise and creative ideas to Bang \& Olufsen, contributing to extraordinary sound experiences that resonate with your company’s values. I would be thrilled to discuss how my skills align with your team’s goals in a personal interview.
\vspace{1em}\\
\noindent Sincerely,\\
Aron Petritz
\vspace{0.5em}\\
+43 664 1000777\\
\href{aronrocco@posteo.net}{aronrocco@posteo.net}

\end{document}
